CommonMind Consortium: DLPFC

### 2020-09-20 combined_analysis/diff.networks.Rmd
Update diff networks

```{r load.dream}
fit_marginal.lst = readRDS(synGet('syn22416500')$path)
fit_inter_sex.disease.lst = readRDS(synGet('syn22416524')$path)
```

@@

df_module_enrich.Sex = enrich.test( df_module.Sex, go.gs, df_cohort2$Module[i])
```

@@

@@

df_module_enrich.Dx = enrich.test( df_module.Dx, go.gs, df_cohort2$Module[i])
```

@@

@@

df_module_enrich.Dx_Sex = enrich.test( df_module.Dx_Sex, go.gs, df_cohort2$Module[i])
```

@@

>>>>

```{r load.dream}
fit_marginal.lst = readRDS(synGet('syn22416500')$path)
fit_inter_sex.disease.lst = readRDS(synGet('syn22416524')$path)
df_meta = readRDS(synGet('syn22416508')$path)
df_meta.inter_sex.disease = readRDS(synGet('syn22416532')$path)
```

@@

df_module_enrich.Sex = enrich.test( df_module.Sex, go.gs, df_cohort2$Module[i], 150).  
```

@@

## DE enrichment
```{r cameraPR.Sex}
res_enrich_DE = enrich_module_DE( df_module.Sex )

figList = lapply( df_cohort2$Module[i], function(module){

	res = res_enrich_DE[res_enrich_DE$Geneset == module,]

	ggplot(res, aes(Test, -log10(PValue))) + geom_bar(stat="identity", fill=res$Geneset[1]) + coord_flip() + theme_bw() + theme(aspect.ratio=1, plot.title = element_text(hjust = 0.5))  + scale_y_continuous(expand=c(0,0)) + ggtitle(module)
}) 
plot_grid(plotlist = figList, ncol=1)
```

@@

df_module_enrich.Dx = enrich.test( df_module.Dx, go.gs, df_cohort2$Module[i], 150)
```

@@

## DE enrichment
```{r cameraPR.Dx}
res_enrich_DE = enrich_module_DE( df_module.Dx )

figList = lapply( df_cohort2$Module[i], function(module){

	res = res_enrich_DE[res_enrich_DE$Geneset == module,]

	ggplot(res, aes(Test, -log10(PValue))) + geom_bar(stat="identity", fill=res$Geneset[1]) + coord_flip() + theme_bw() + theme(aspect.ratio=1, plot.title = element_text(hjust = 0.5))  + scale_y_continuous(expand=c(0,0)) + ggtitle(module)
}) 
plot_grid(plotlist = figList, ncol=1)
```

@@

df_module_enrich.Dx_Sex = enrich.test( df_module.Dx_Sex, go.gs, df_cohort2$Module[i], 150)
```

@@

## DE enrichment
```{r cameraPR.Dx_Sex}
res_enrich_DE = enrich_module_DE( df_module_enrich.Dx_Sex )

figList = lapply( df_cohort2$Module[i], function(module){

	res = res_enrich_DE[res_enrich_DE$Geneset == module,]

	ggplot(res, aes(Test, -log10(PValue))) + geom_bar(stat="identity", fill=res$Geneset[1]) + coord_flip() + theme_bw() + theme(aspect.ratio=1, plot.title = element_text(hjust = 0.5))  + scale_y_continuous(expand=c(0,0)) + ggtitle(module)
}) 
plot_grid(plotlist = figList, ncol=1)
```
